Planetary perturbers: Flaring star-planet interactions in Kepler and TESS

### 2023-06-23 src/tex/ms.tex
[showyourwork] overleaf sync

% Title
\title{Planetary perturbers, or: flaring star-planet interactions in Kepler and TESS}

@@

\begin{figure*}[ht!]
\script{paper_illustrative_sketch_of_system_geometries.py}
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{figures/system_geometries.png}
        \caption{
         Simplified magnetic star-planet interaction (SPI) viewing geometries. The hatched hemisphere is visible to the observer. \textbf{ Panel a: Fully aligned system along the line of sight (LOS). } Magnetic, rotational, and orbital axis are aligned. The interaction footpoint moves along the black line, and is visible to the observer on the red latitude, i.e. during $50\%$ of the planet's orbit. Flares induced along this latitude will result in excess flares when the planet is in front of the star \textbf{Panel b: Inclined fully aligned system.} The interaction footpoint latitude is visible $100\%$ of the time. No modulation due to magnetic SPI can be observed, even if flares are triggered by the planet. The sketches only show the interaction on one hemisphere of the star, but they may appear on both. More complicated geometries arise when orbital, rotational and magnetic axis are mutually misaligned. The two panels also illustrate how a planet in a closer orbit interacts at a lower latitude than a farther out planet. }
        \label{fig:sketch}
    \end{centering}
\end{figure*}

>>>>

% Title
\title{Planetary perturbers: Flaring star-planet interactions in Kepler and TESS}

@@

\begin{figure*}[ht!]
\script{paper_illustrative_sketch_of_system_geometries.py}
    \begin{centering}
        \includegraphics[width=0.7\linewidth]{figures/system_geometries.png}
        \caption{
         Simple magnetic star-planet interaction (SPI) viewing geometries. \textbf{a.: system aligned along the line of sight (LOS). } The interaction footpoint moves along the black line, and is on the visible hemisphere (hatched area) for $50\%$ of the  orbit (red line). Flaring SPI can be observed as modulation of flare occurrence times. \textbf{b.: Inclined system.} The interaction latitude is visible $100\%$ of the time, so no modulation can be observed. Interaction is shown on one hemisphere, but may appear on both. Complex geometries arise when orbital, rotational and magnetic axis are misaligned. The panels also illustrate how a planet in a closer orbit (a.) interacts at a lower latitude than a farther out planet (b.). }
        \label{fig:sketch}
    \end{centering}
\end{figure*}
